JMS

### 2021-04-12 analysis.Rmd
Update analysis.Rmd
simplified image (no scatterplot)

# Change work directory in quotes
setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")

@@

plotname <- "images/vllblc.jpg"
xlab_t <- "ß value liberal local"

@@

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL,
  scale = 1,
  width = 12,
  height = 9,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/vllbmn.jpg"
xlab_t <- "ß value liberal minority"

@@

@@

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL,
  scale = 1,
  width = 12,
  height = 9,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/et_libloc.jpg"
xlab_t <- "ß ethnic liberal local"

xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)

 expo_pic <-   ggplot(data = etlib_df) + 
  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +

   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +

    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +

  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
  xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL,
  scale = 1,
  width = 12,
  height = 9,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/et_libmin.jpg"
xlab_t <- "ß ethnic liberal minority"

xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)

 expo_pic <-   ggplot(data = etlib_df) + 
  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +

   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +

    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +

  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +

>>>>

# Add working directory, substitute * in quotes (leave "/" for folders output of images and latex, or tweak). If bug with output name "images/" or "latex/", delete them in the name of output

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/")

@@

plotname <- "images/vllblc.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal local"

# deleted scatterplot

# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
#        dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
# 
#  expo_pic <-   ggplot(data = dataset_sa) + 
#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
#

@@

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "right", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

#, plot.caption = element_text(hjust= 0.5, size = 11)
# ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL, 
  scale = 1,
  width = 7.5,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/vllbmn.jpg"  # delete images/ if bug
xlab_t <- "ß value liberal minority"

# deleted scatterplot

# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
       # dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)

@@

#  expo_pic <-   ggplot(data = dataset_sa) + 
#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "right", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

#, plot.caption = element_text(hjust= 0.5, size = 11)
# ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL,
  scale = 1,
  width = 7.5,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/et_libloc.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal local"

# deleted scatterplot

# xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
#        etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
# 
#  expo_pic <-   ggplot(data = etlib_df) + 
#   geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#   xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
#

@@

prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "right", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

#, plot.caption = element_text(hjust= 0.5, size = 11)
# ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))

ggsave(plotname,plot = last_plot(),
  device = NULL,path = NULL,
  scale = 1,
  width = 7.5,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

@@

plotname <- "images/et_libmin.jpg" # delete images/ if bug
xlab_t <- "ß ethnic liberal minority"

# deleted scatterplot

# xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
#        etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
# 
#  expo_pic <-   ggplot(data = etlib_df) + 
#   geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
#   geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
#   geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
# 
#   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
#    geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
#   
#    geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
#   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
#   
#     geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
#   geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
#   
#   geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
# geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
#   
#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
#   geom_vline(xintercept = 1, color = "red") +
#   xlab(expression(Exposure[correct])) + ylab("Exposure") +
#   theme_bw() + theme( 
#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
#  
# 
data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
